Advancements in Moltres for Time-Dependent Multiphysics Molten Salt Reactor Modeling

### 2024-11-26 transient.tex
Flowchart & u233 temp coef

\begin{figure}[htb!]
  \centering
%  \includegraphics[width=0.8\columnwidth]{rod-height}
  \caption{The nested iteration structure coupling the $S_N$, neutron diffusion, and \gls{DNP}
  solvers for the rod drop simulation using the hybrid $S_N$-diffusion method.}
  \label{fig:rod-drop-coupling}
\end{figure}

@@

For the isotopic content of uranium, I used a composition restruction strategy developed by Burke
\cite{burke_analysis_2019}. Their analysis determined that the $^{233}$U salt consists of residual
salt from $^{235}$U operations, a depleted uranium feed, and a stock $^{233}$U feed. The residue
and depleted uranium feed masses, taken from Burke's work, are 1.935 kg and 0.890 kg, respectively.
The stock feed uranium
mass is estimated to be 35.234 kg reported on January 12 1969 \cite{thoma_chemical_1971}. The
experiment was performed on January 16 1969 \cite{steffy_experimental_1970}. Table * shows
the breakdown and total isotopic content of uranium in the salt. The density of $^{233}$U salt is
2.264 g cm$^{-3}$ at 911 K \cite{thoma_chemical_1971}.
%
\begin{table}[t]
  \small
  \centering
  \setlength\tabcolsep{4pt}
  \caption{Uranium isotopic composition reconstruction table \cite{burke_analysis_2019}.}
  \begin{tabular}{l S S S S S S S}
    \toprule
    \multirow{2}{*}{Uranium Source} & {\multirow{2}{*}{Mass [kg]}} & \multicolumn{6}{c}{Weight percentage [\%]} \\
                                    & & {$^{232}$U} & {$^{233}$U} & {$^{234}$U} & {$^{235}$U} & {$^{236}$U} & {$^{238}$U} \\
                                    \cmidrule(r){1-1} \cmidrule(rl){2-2} \cmidrule(l){3-8}
    Residue & 1.935 & & & 0.343 & 32.705 & 0.483 & 66.469 \\
    Depleted & 0.890 & & & & 0.3 & & 99.7 \\
    Stock & 35.234 & 0.02 & 91.49 & 7.6 & 0.7 & 0.05 & 0.14 \\
    \bottomrule
  \end{tabular}
  \label{table:u233-composition}
\end{table}

@@

\begin{figure}[htb!]
  \centering
%  \includegraphics[width=0.8\columnwidth]{rod-height}
  \caption{The nested iteration structure coupling the $S_N$, neutron diffusion,
  \gls{DNP}-temperature, and out-of-core
  solvers for the rod drop simulation using the hybrid $S_N$-diffusion method.}
  \label{fig:insertion-coupling}
\end{figure}

@@

>>>>

\begin{figure}[t]
  \tikzstyle{every node}=[font=\small]
  \centering
  \begin{tikzpicture}
    \node (1) [solver] {\textbf{$\bm{S_N}$ transport subsolver}};
    \node (2) [solver, right of=1, xshift=4cm] {\textbf{Neutron\\ diffusion\\ subsolver}};
    \node (3) [solver, right of=2, xshift=4cm] {\textbf{DNP \& temperature subsolver}};
    \draw [arrow] (1.10) -- node[anchor=south, text width=4cm, align=center] {$\vec{D}_g, \gamma_g$} (2.170);
    \draw [arrow] (2.190) -- node[anchor=north, text width=4cm, align=center] {$\phi_g, C_i, T$} (1.350);
    \draw [arrow] (2.10) -- node[anchor=south, text width=4cm, align=center] {$Q_f, Q$} (3.170);
    \draw [arrow] (3.190) -- node[anchor=north, text width=4cm, align=center] {$C_i, T$} (2.350);
    \node (5) [bound, fit=(2) (3), inner sep=8pt, label={[align=left]above:\textbf{Inner iteration}}] {};
    \node (6) [bound, fit=(1) (5), inner sep=15pt, label={[align=left]above:\textbf{Outer iteration}}] {};
  \end{tikzpicture}
  \caption{The nested iteration structure coupling the $S_N$, neutron diffusion, and \gls{DNP}
  solvers for the rod drop simulation using the hybrid $S_N$-diffusion method.}
  \label{fig:rod-drop-coupling}
\end{figure}

@@

For the isotopic content of uranium, I used a composition restruction strategy developed by Burke
\cite{burke_analysis_2019}. Their analysis determined that the $^{233}$U salt consists of residual
salt from $^{235}$U operations, a depleted uranium feed, and a stock $^{233}$U feed. The residue
and depleted uranium feed masses, taken from Burke's work, are 1.935 kg and 0.890 kg, respectively.
The stock feed uranium
mass is estimated to be 35.234 kg reported on January 12 1969 \cite{thoma_chemical_1971}. The
experiment was performed on January 16 1969 \cite{steffy_experimental_1970}. Table 
\ref{table:u233-composition} shows
the breakdown and total isotopic content of uranium in the salt. The density of $^{233}$U salt is
2.264 g cm$^{-3}$ at 911 K \cite{thoma_chemical_1971}.
%
\begin{table}[t]
  \small
  \centering
  \setlength\tabcolsep{4pt}
  \caption{Uranium isotopic composition reconstruction table \cite{burke_analysis_2019}.}
  \begin{tabular}{l S S S S S S S}
    \toprule
    \multirow{2}{*}{Uranium Source} & {\multirow{2}{*}{Mass [kg]}} & \multicolumn{6}{c}{Weight percentage [\%]} \\
                                    & & {$^{232}$U} & {$^{233}$U} & {$^{234}$U} & {$^{235}$U} & {$^{236}$U} & {$^{238}$U} \\
                                    \cmidrule(r){1-1} \cmidrule(rl){2-2} \cmidrule(l){3-8}
    Residue & 1.935 & & & 0.343 & 32.705 & 0.483 & 66.469 \\
    Depleted & 0.890 & & & & 0.3 & & 99.7 \\
    Stock & 35.234 & 0.02 & 91.49 & 7.6 & 0.7 & 0.05 & 0.14 \\
    \bottomrule
  \end{tabular}
  \label{table:u233-composition}
\end{table}

@@

\begin{figure}[t]
  \tikzstyle{every node}=[font=\small]
  \centering
  \begin{tikzpicture}
    \node (1) [solver] {\textbf{$\bm{S_N}$ transport subsolver}};
    \node (2) [solver, right of=1, xshift=4cm] {\textbf{Neutron\\ diffusion\\ subsolver}};
    \node (3) [solver, right of=2, xshift=4cm] {\textbf{In-core DNP \& temperature subsolver}};
    \node (4) [solver, below of=3, yshift=-3cm] {\textbf{Ex-core DNP \& temperature subsolver}};
    \draw [arrow] (1.10) -- node[anchor=south, text width=4cm, align=center] {$\vec{D}_g, \gamma_g$} (2.170);
    \draw [arrow] (2.190) -- node[anchor=north, text width=4cm, align=center] {$\phi_g, C_i, T$} (1.350);
    \draw [arrow] (2.10) -- node[anchor=south, text width=4cm, align=center] {$Q_f, Q$} (3.170);
    \draw [arrow] (3.190) -- node[anchor=north, text width=4cm, align=center] {$C_i, T$} (2.350);
    \draw [arrow] (3.280) -- node[anchor=west, text width=1cm, align=center] {$C^\text{out}_i$\\ $T^\text{out}$} (4.80);
    \draw [arrow] (4.100) -- node[anchor=east, text width=1cm, align=center] {$C^\text{in}_i$\\ $T^\text{in}$} (3.260);
    \node (5) [bound, fit=(3) (4), label={[align=center,rotate=90]left:\textbf{Salt loop}\\}] {};
    \node (6) [bound, fit=(2) (5), label={[align=center,rotate=90]left:\textbf{Inner iteration}\\}] {};
    \node (7) [bound, fit=(1) (6), label={[align=center,rotate=90]left:\textbf{Outer iteration}\\}] {};
  \end{tikzpicture}
  \caption{The nested iteration structure coupling the $S_N$, neutron diffusion,
  in-core \gls{DNP}-temperature, and ex-core
  solvers for the reactivity insertion simulation using the hybrid $S_N$-diffusion method.}
  \label{fig:insertion-coupling}
\end{figure}

@@

\subsection{Temperature Reactivity Coefficient}

This work compares isothermal temperature reactivity coefficients calculated from $k_\text{eff}$
values measured at 872 K and 972 K with the $^{233}$-fueled \gls{MSRE} at operating fuel
concentration. This approach is identical to that
of the \gls{MSRE} experimental measurements \cite{engel_zero-power_1972} and the temperature
coefficient calculation procedure used for the $^{235}$U-fueled \gls{MSRE} in Section
\ref{sec:temp-coef}.

Table \ref{table:temp-coef-u233} compares the isothermal reactivity coefficients from the experimental
and numerical sources. No uncertainty data is available from the relevant \gls{ORNL} report
\cite{engel_zero-power_1972}. However, the authors noted significantly different readings ranging
from 12.4 to 15.3 pcm K$^{-1}$ due to gas bubbles introduced by the salt pump. The
presence of gas bubbles led to smaller reactivity coefficient measurements. The numerical OpenMC
and hybrid models overestimate the temperature reactivity coefficient magnitude by 12 \% and 11 \%,
respectively, relative to the experimental data.

\begin{table}[t]
  \small
  \centering
  \caption{Isothermal temperature reactivity coefficients with $^{233}$U-fueled \gls{MSRE} from
    \gls{MSRE} experimental data, \gls{MSRE} predicted value, and the OpenMC
  and Moltres models in this work.}
  \begin{tabular}{l S[separate-uncertainty=true,table-format=2.2(2)] S}
    \toprule
     & {Temperature coefficient [pcm K$^{-1}$]} & {Percentage discrepancy [\%]}\\
     \cmidrule(rl){2-2} \cmidrule(l){3-3}
    \gls{MSRE} experimental data & -15.3 & {-}\\
    \gls{MSRE} predicted value & -15.8 & -3.4 \\
    OpenMC (This work) & -17.14 & -12 \\
    Hybrid (This work) & -16.96 & -11 \\
    \bottomrule
  \end{tabular}
  \label{table:temp-coef-u233}
\end{table}
